Price of Anarchy for Mean Field Games

### 2018-07-23 PoA.tex
finished Proposition 7 case 3, limit of h(b_1)
update prop 6 second half

	Since $u_t^{b_2}$, $w_t^{b_2}$ and $\bar{x}_t^{MFG,b_2}$ are continuous functions on $[0,T]$, we deduce that the functions $\displaystyle t \mapsto \int_0^t u_s^{b_2} ds$ and $\displaystyle t \mapsto \int_0^t (u_s^{b_2}- w_s^{b_2})^2 (\bar{x}_s^{MFG,b_2})^2 ds$ are continuous on $[0,T]$ and differentiable on $(0,T)$. Then with equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we can apply the Mean Value Theorem so that there exists two fixed times $0 < t_2 < t_1 < T$ for which
	\begin{IEEEeqnarray}{rCl}
		\Delta SC &=& \frac{1}{2} B^{b_2} \int_0^T (u^{b_2}_t- w^{b_2}_t)^2 (\bar{x}_t^{MFG,b_2} )^2 dt  \nonumber \\
		&=& \frac{1}{2} B^{b_2}  (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 (\bar{x}_{t_1}^{MFG,b_2} )^2  \cdot T \nonumber \\
		&=& \frac{T  B^{b_2} }{2} \cdot (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{b_2} u_s^{b_2} ds \right) \nonumber \\
		&=&  \kappa_1 \left[ (b_2 + \bar{b}_2) (u_{t_1}^{b_2}- w_{t_1}^{b_2} ) \right]^2\cdot  \exp \left( - 2 B^{b_2} u_{t_2}^{b_2} \cdot t_1 \right) \nonumber \\
		&= & \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 \cdot  e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)},
		\label{eq:delta_SC_b_2_infty}
	\end{IEEEeqnarray}
	where  $\displaystyle \kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ and $\displaystyle \kappa_2 = \frac{2 t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ are two positive constants independent of $b_2$.\\

	Similarly, with equation (\ref{eq:v_t_new_notation}) of the variance $v_t$, we know that the functions $t \mapsto v_t$ and $\displaystyle t \mapsto \int_0^t (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds $ are continuous on $[0,T]$ and differentiable on $(0,T)$. Then the Mean Value Theorem yields that there exists a time  $t_3 \in (0,T)$ so that 
	\begin{equation}
	 \int_0^T (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds = \left(q + \bar{q} + \frac{1}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) v_{t_3}^{b_2} \cdot T,
	\label{eq:vt_int_b_2_infinity}
	\end{equation}
	and	there exists 3 time points $t_4, t_5, t_6$ satisfying $0<t_4 < T$ and $0 < t_5 < t_6 < T$ so that
	\begin{IEEEeqnarray}{rCl}
		v^{b_2}_T &=& Var(\xi) \exp \left( 2 \int_0^T (b_1 - B^{\eta,b_2} \eta_s^{b_2}) ds \right) + \sigma^2 \int_0^T \exp \left(2 \int_s^T (b_1 - B^{\eta,b_2} \eta_u^{b_2}) du \right)	ds \nonumber \\
		&=& Var(\xi) e^{2b_1 T} \exp \left(-2 B^{\eta,b_2} \eta_{t_4}^{b_2} \cdot T \right) + \sigma^2 \exp\left(2 \int_{t_5}^T (b_1 - B^{\eta,b_2} \eta_u^{b_2}) du \right) \cdot T \nonumber \\
		&=&  Var(\xi) e^{2b_1 T} e^{-\frac{2T}{r+\bar{r}} b_2 h_\eta(b_2,t_4)} + \sigma^2 T e^{2b_1 (T-t_5)} \exp \left( -2 B^{\eta,b_2} \eta_{t_6}^{b_2} (T-t_5) \right) \nonumber \\
		&=& \kappa_3 e^{-\kappa_4 b_2 h_\eta(b_2,t_4)} + \kappa_5 e^{-\kappa_6 b_2 h_\eta(b_2,t_6)}
	\label{eq:vt_b_2_infinity} 
	\end{IEEEeqnarray}
	where
	$\displaystyle \kappa_3 = Var(\xi) e^{2b_1 T}, \  \kappa_4 = \frac{2T}{r+\bar{r}},\  \kappa_5 = \sigma^2 T e^{2b_1(T-t_5)}, \   \kappa_6 = \frac{2(T-t_5)}{r+ \bar{r}}$ are four positive constants independent of $b_2$.

@@

	With equation (\ref{eq:delta_SC_b_2_infty}) and (\ref{eq:vt_int_b_2_infinity}), we can multiply $\Delta SC$ and $SC^{MKV}$ by $(b_2 +\bar{b}_2)$ and then deduce that
	\begin{IEEEeqnarray}{rCl}
		\frac{\Delta SC}{SC^{MKV}} &=& \frac{\displaystyle \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 \cdot  e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)} }{\displaystyle \left( (q + \bar{q})T + \frac{T}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) v_{t_3}^{b_2} + (q_T + \bar{q}_T) v_T^{b_2} + \frac{1}{b_2+\bar{b}_2} (\mathbb{E}(\xi) )^2 h_w(b_2,0)  } \nonumber \\
		&=& \frac{l_{u,v}(b_2) \cdot (b_2 + \bar{b}_2) e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)}} { l_\eta(b_2) \cdot b_2 v_{t_3}^{b_2}  + l_1(b_2) \cdot b_2 v_T^{b_2} + (\mathbb{E}(\xi))^2 h_w(b_2,0) }
	\label{eq:delta_SC_SC^MKV_b_2_infinity}
	\end{IEEEeqnarray}
	where 
	$\displaystyle l_{u,v}(b_2) = \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 , \  l_\eta(b_2) =  \left( (q + \bar{q})T + \frac{T}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) \frac{b_2 + \bar{b}_2}{b_2}$
	and $\displaystyle l_1(b_2) = (q_T + \bar{q}_T) \frac{b_2 + \bar{b}_2}{b_2}$.	
	With the limits of $h_u(b_2,t), h_w(b_2,t)$ and $h_\eta(b_2,t)$ for any fixed $t \in [0,T)$, it is easy to check that 
	$$ l_{u,v}(b_2,t_3) \xrightarrow[b_2 \to \infty]{} \kappa_1 (c_3 - c_4)^2, \quad l_\eta(b_2) \xrightarrow[b_2 \to \infty]{} (q+ \bar{q} + \frac{c_5^2}{r+ \bar{r}})T,\quad l_1(b_2) \xrightarrow[b_2 \to \infty]{} q_T + \bar{q}_T.$$

	Finally, we will show that for any fixed $t \in [0,T)$ and $\kappa >0$, we have
	\begin{equation}
		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2) h_u(b_2,t)} \xrightarrow[b_2 \to \infty]{} 0 \qquad \text{and} \qquad b_2 e^{-\kappa b_2 h_\eta(b_2, t)} \xrightarrow[b_2 \to \infty]{} 0.
	\label{eq:b_2_vt_limit}
	\end{equation}
	Therefore, the numerator of equation (\ref{eq:delta_SC_SC^MKV_b_2_infinity}) tends towards $0$ whilst the denominator tends towards $(\mathbb{E}(\xi))^2 c_4>0$ because equation (\ref{eq:vt_b_2_infinity}) gives raise to
	$$ b_2 v_T^{b_2} = \kappa_3 \cdot b_2 e^{-\kappa_4 b_2 h_\eta(b_2,t_4)} + \kappa_5 \cdot b_2 e^{-\kappa_6 b_2 h_\eta(b_2,t_6)} \xrightarrow[b_2 \to \infty]{} 0,$$
	and so $b_2 v_{t_3}^{b_2} \xrightarrow[b_2 \to \infty]{} 0$.
	Together with the limits of $l_{u,v}(b_2), l_\eta(b_2)$ and $l_1(b_2)$, we have
	$$ \frac{\Delta SC}{SC^{MKV}} \xrightarrow[b_2 \to \infty]{} 0.$$

@@

	Now, let's assume $\bar{b}_2 > 0$.	As $b_2 \to 0$, we have 
	\begin{equation*}
	\begin{array}{l}
		\lambda \longrightarrow 0\\
		\displaystyle B^{b_2} \longrightarrow{}  \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{b_2 \to 0} >0, \qquad B^{\eta,b_2} \longrightarrow{} 0 \\
		C^{u,b_2} \longrightarrow{} 0, \  D^{u,b_2} \longrightarrow{} 0 
	\end{array}
	\end{equation*}
	and $A^u, (A^w, C^w, D^w), (A^\eta, C^\eta, D^\eta)$ are independent of $b_2$.
	Moreover, we have $\delta^{+,b_2}_u \xrightarrow{} -2A^u >0 $ and $\delta^{-,b_2}_u \to 0$, so that $\delta^{+}_u - \delta^{-}_u \xrightarrow{} -2 A^u > 0$. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
	$$u^{b_2}_t \xrightarrow[b_2 \to 0 ]{} 0 .$$
	Similar to the case in Proposition \ref{prop:r_bar_r}, we can derive an uniform bound for $u_t^{b_2}$ over $[0,T]$ for any $b_2$ small enough. Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 \leq b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
	\begin{equation*}
	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } =: c_2 ,\qquad \forall  \  t \in [0,T]
	\end{equation*}

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$
	then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	First, we consider $\bar{b}_2 \to 0$. For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.

@@

	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda^{\bar{b}_2} \to 0$
	and $B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0$. It can be shown that:
	$$\lim_{\bar{b}_2 \to \infty}C^{u,\bar{b}_2}\sqrt{b_2+\bar{b}_2}=0,$$
	and
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},$$
	and therefore,
	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty \qquad \text{and } \qquad \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
	Also, note from the assumptions $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$, we have $D^u>0$ and $D^w>0$. From equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
	\begin{equation*}
	\begin{split}
	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
	 	& \xrightarrow[\bar{b}_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) c_{\delta^{\bar{b}_2 \to \infty}_u}=: c_3,
	 \end{split} 
	\end{equation*}
	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$.

>>>>

	Since $u_t^{b_2}$, $w_t^{b_2}$ and $\bar{x}_t^{MFG,b_2}$ are continuous functions on $[0,T]$, we deduce that the functions $\displaystyle t \mapsto \int_0^t u_s^{b_2} ds$ and $\displaystyle t \mapsto \int_0^t (u_s^{b_2}- w_s^{b_2})^2 (\bar{x}_s^{MFG,b_2})^2 ds$ are continuous on $[0,T]$ and differentiable on $(0,T)$. Then with equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we can apply the Mean Value Theorem so that there exists two fixed times $0 < t_2 < t_1 < T$ depending on $b_2$ for which
	\begin{IEEEeqnarray}{rCl}
		\Delta SC &=& \frac{1}{2} B^{b_2} \int_0^T (u^{b_2}_t- w^{b_2}_t)^2 (\bar{x}_t^{MFG,b_2} )^2 dt  \nonumber \\
		&=& \frac{1}{2} B^{b_2}  (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 (\bar{x}_{t_1}^{MFG,b_2} )^2  \cdot T \nonumber \\
		&=& \frac{T  B^{b_2} }{2} \cdot (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{b_2} u_s^{b_2} ds \right) \nonumber \\
		&=&  \kappa_1 \left(u_{t_1}^{b_2}- w_{t_1}^{b_2} \right)^2\cdot   (b_2 + \bar{b}_2)^2 \exp \left( - 2 B^{b_2} u_{t_2}^{b_2} \cdot t_1 \right) \nonumber \\
		&=& \kappa_1 \left(u_{t_1}^{b_2}- w_{t_1}^{b_2} \right)^2 \cdot (b_2 + \bar{b}_2)^2 e^{-\kappa_2 (b_2+ \bar{b}_2)h_u(b_2,t_2)}
		\label{eq:delta_SC_b_2_infty}
	\end{IEEEeqnarray}
	where  $\displaystyle \kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ and $\displaystyle \kappa_2 = \frac{2 t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ are two positive constants independent of $b_2$.\\

	Similarly, with equation (\ref{eq:v_t_new_notation}) of the variance $v_t$, we know that the functions $t \mapsto v_t$ and $\displaystyle t \mapsto \int_0^t (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds $ are continuous on $[0,T]$ and differentiable on $(0,T)$. Then the Mean Value Theorem yields that there exists a time point $t_3 \in (0,T)$ depending on $b_2$ so that 
	\begin{equation}
	 \int_0^T (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds = (q + \bar{q} ) T v_{t_3}^{b_2} +  \frac{T}{r + \bar{r}} (\eta_{t_3}^{b_2})^2 \cdot b_2^2 v_{t_3}^{b_2},
	\label{eq:vt_int_b_2_infinity}
	\end{equation}
	and	there exists 3 time points $t_4, t_5, t_6$ satisfying $0<t_4 < T$ and $0 < t_5 < t_6 < T$ so that
	\begin{IEEEeqnarray}{rCl}
		v^{b_2}_T &=& Var(\xi) \exp \left( 2 \int_0^T (b_1 - B^{\eta,b_2} \eta_s^{b_2}) ds \right) + \sigma^2 \int_0^T \exp \left(2 \int_s^T (b_1 - B^{\eta,b_2} \eta_u^{b_2}) du \right)	ds \nonumber \\
		&=& Var(\xi) e^{2b_1 T} \exp \left(-2 B^{\eta,b_2} \eta_{t_4}^{b_2} \cdot T \right) + \sigma^2 \exp\left(2 \int_{t_5}^T (b_1 - B^{\eta,b_2} \eta_u^{b_2}) du \right) \cdot T \nonumber \\
		&=&  Var(\xi) e^{2b_1 T} e^{-\frac{2T}{r+\bar{r}} b_2 h_\eta(b_2,t_4)} + \sigma^2 T e^{2b_1 (T-t_5)} \exp \left( -2 B^{\eta,b_2} \eta_{t_6}^{b_2} (T-t_5) \right) \nonumber \\
		&=& \kappa_3 e^{-\kappa_4 b_2 h_\eta(b_2,t_4)} + \kappa_5 e^{-\kappa_6 b_2 h_\eta(b_2,t_6)}
	\label{eq:vt_b_2_infinity} 
	\end{IEEEeqnarray}
	where
	$\displaystyle \kappa_3 = Var(\xi) e^{2b_1 T}, \  \kappa_4 = \frac{2T}{r+\bar{r}},\  \kappa_5 = \sigma^2 T e^{2b_1(T-t_5)}, \   \kappa_6 = \frac{2(T-t_5)}{r+ \bar{r}}$ are four positive constants independent of $b_2$.

@@

	With equation (\ref{eq:delta_SC_b_2_infty}) and (\ref{eq:vt_int_b_2_infinity}), we can multiply $\Delta SC$ and $SC^{MKV}$ by $(b_2 +\bar{b}_2)$ and then deduce that
	\begin{IEEEeqnarray}{rCl}
		\frac{\Delta SC}{SC^{MKV}} &=& \frac{\displaystyle \kappa_1 \left(u_{t_1}^{b_2}- w_{t_1}^{b_2} \right)^2 \cdot (b_2 + \bar{b}_2)^2 e^{-\kappa_2 (b_2+ \bar{b}_2)h_u(b_2,t_2)} }{\displaystyle (q + \bar{q} ) T v_{t_3}^{b_2} +  \frac{T}{r + \bar{r}} (\eta_{t_3}^{b_2})^2 \cdot b_2^2 v_{t_3}^{b_2} + (q_T + \bar{q}_T) v_T^{b_2} + \frac{1}{b_2+\bar{b}_2} (\mathbb{E}(\xi) )^2 h_w(b_2,0)  } \nonumber \\
		&=& \frac{l_{u,v}(b_2) \cdot (b_2 + \bar{b}_2)^3 e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)}} { l_{\eta,1}(b_2) \cdot b_2 v_{t_3}^{b_2}  + l_{\eta,2}(b_2)\cdot b_2^3 v_{t_3}^{b_2}+ l_{\eta,3}(b_2) \cdot b_2 v_T^{b_2} + (\mathbb{E}(\xi))^2 h_w(b_2,0) }
	\label{eq:delta_SC_SC^MKV_b_2_infinity}
	\end{IEEEeqnarray}
	where 
	$\displaystyle l_{u,v}(b_2) = \kappa_1   \left(u_{t_1}^{b_2}- w_{t_1}^{b_2} \right)^2 $, and
	$$ \displaystyle l_{\eta,1}(b_2) =  (q + \bar{q})T  \frac{b_2 + \bar{b}_2}{b_2},\quad 
	l_{\eta,2}(b_2) = \frac{T}{r+ \bar{r}} (\eta_{t_3}^{b_2})^2 \frac{b_2 + \bar{b}_2}{b_2}, \quad 
	l_{\eta,3}(b_2) = (q_T + \bar{q}_T) \frac{b_2 + \bar{b}_2}{b_2}.$$

	It is not hard to show that $u_t^{b_2}, w_t^{b_2}$ and $\eta_t^{b_2}$ are uniformly bounded over $[0,T]$ for any $b_2$ being large enough. One way is to follow the same technique shown in Proposition \ref{prop:r_bar_r} to derive these uniform upper bounds. Indeed, for any fixed $b_2$, the solution $(u_t^{b_2})_{0\leq t \leq T}$ is increasing along $[0,T]$ when $B^{b_2} (D^{u,b_2})^2 + 2 A^{u} D^{u,b_2} - C^{u,b_2} > 0$. As $B^{b_2} \to \infty, C^{u,b_2} \to C^{u,b_2 \to \infty}$ and $D^{u,b_2} \to D^{u,b_2\to \infty}$, there must exist $b_2^*> 0 $ so that
	$$\sup_{b_2 \geq b_2^*} \sup_{0 \leq t \leq T} \{ u_t^{b_2}\} \leq \sup_{b_2 \geq b_2^*} \{ u_T^{b_2} \} = \sup_{b_2 \geq b_2^*} \{ D^{u,b_2} \} \leq D^{u,b_2\to \infty} + 1.$$
	Thus, there exists a constant $M$ independent of $b_2$ such that for any large enough $b_2$:
	$$ \max \{ l_{u,v}(b_2), \  l_{\eta,1}(b_2), \  l_{\eta,2}(b_2), \  l_{\eta,3}(b_2) \} \leq M.$$

	\begin{comment}
	With the limits of $h_u(b_2,t), h_w(b_2,t)$ and $h_\eta(b_2,t)$ for any fixed $t \in [0,T)$, it is easy to check that 
	$$ l_{u,v}(b_2,t_3) \xrightarrow[b_2 \to \infty]{} \kappa_1 (c_3 - c_4)^2, \quad l_\eta(b_2) \xrightarrow[b_2 \to \infty]{} (q+ \bar{q} + \frac{c_5^2}{r+ \bar{r}})T,\quad l_1(b_2) \xrightarrow[b_2 \to \infty]{} q_T + \bar{q}_T.$$
	\end{comment}

	Finally, we will show that for any $p > 0$ and $\kappa >0$, we have
	\begin{equation}
	\begin{array}{ll}
		& \displaystyle (b_2 + \bar{b}_2)^p \exp \left( - \kappa (b_2 + \bar{b}_2) \min_{0 \leq t \leq T} h_u(b_2,t) \right) \xrightarrow[b_2 \to \infty]{} 0 \\
		and \quad & \displaystyle b_2^p \exp \left( -\kappa b_2 \min_{0 \leq t \leq T} h_\eta(b_2, t) \right) \xrightarrow[b_2 \to \infty]{} 0.
	\end{array}
	\label{eq:b_2_vt_limit}
	\end{equation}
	Therefore, the numerator of equation (\ref{eq:delta_SC_SC^MKV_b_2_infinity}) tends towards $0$ because
	$$ (b_2 + \bar{b}_2)^3 e^{-\kappa_2 (b_2+ \bar{b}_2) h_u(b_2,t_2)} \leq (b_2 + \bar{b}_2)^3 e^{- \kappa (b_2 + \bar{b}_2) \min_{0 \leq t \leq T} h_u(b_2,t)}.
	$$
	Meanwhile, the denominator tends towards $(\mathbb{E}(\xi))^2 c_4>0$, because 
	$$ h_w(b_2,0) = b_2 \eta_0^{b_2} \xrightarrow[b_2 \to \infty]{} c_4,$$
	and equation (\ref{eq:vt_b_2_infinity}) gives raise to
	\begin{IEEEeqnarray*}{rCl} 
		b_2 v_T^{b_2} &=& \kappa_3 \cdot b_2 e^{-\kappa_4 b_2 h_\eta(b_2,t_4)} + \kappa_5 \cdot b_2 e^{-\kappa_6 b_2 h_\eta(b_2,t_6)} \\
		& \leq & (\kappa_3 + \kappa_5) b_2 e^{- \min\{\kappa_4, \kappa_6\} \cdot b_2  \min_{0 \leq t \leq T} h_\eta(b_2, t) } \\
		& \xrightarrow[b_2 \to \infty]{}& 0,
	\end{IEEEeqnarray*}
	and so as for $b_2 v_{t_3}^{b_2} \xrightarrow[b_2 \to \infty]{} 0$ and $b_2^{3} v_{t_3}^{b_2} \xrightarrow[b_2 \to \infty]{} 0$.
	Together with the  we have
	$$ \frac{\Delta SC}{SC^{MKV}} \xrightarrow[b_2 \to \infty]{} 0.$$

@@

	Now, let's assume $\bar{b}_2 > 0$.	As $b_2 \to 0$, we have 
	\begin{equation*}
	\begin{array}{l}
		\lambda \longrightarrow 0\\
		\displaystyle B^{b_2} \longrightarrow{}  \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{b_2 \to 0} >0, \qquad B^{\eta,b_2} \longrightarrow{} 0 \\
		C^{u,b_2} \longrightarrow{} 0, \  D^{u,b_2} \longrightarrow{} 0 
	\end{array}
	\end{equation*}
	and $A^u, (A^w, C^w, D^w), (A^\eta, C^\eta, D^\eta)$ are independent of $b_2$.
	Moreover, we have $\delta^{+,b_2}_u \xrightarrow{} -2A^u >0 $ and $\delta^{-,b_2}_u \to 0$, so that $\delta^{+}_u - \delta^{-}_u \xrightarrow{} -2 A^u > 0$. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
	$$u^{b_2}_t \xrightarrow[b_2 \to 0 ]{} 0 .$$
	Similar to the case in Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for any $b_2$ small enough. Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 \leq b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
	\begin{equation*}
	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } =: c_2 ,\qquad \forall  \  t \in [0,T]
	\end{equation*}

@@

% proposition b2 bar
\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$
	then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	First, we consider $\bar{b}_2 \to 0$. For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.

@@

	Now, for the case when $\bar{b}_2 \to \infty$,  we have 
	\begin{equation*}
	\begin{array}{l}
		\lambda^{\bar{b}_2} \to 0;\\
		B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0
	\end{array}
	\end{equation*}
	and $A^{u}, (A^w,C^w,D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.
	We can show that 
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},$$
	Idem, we can deduce that 
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}}.$$
